\documentclass[11pt, a4paper, draft]{article}
\usepackage[a4paper, total={6.5in, 11in}]{geometry}
\usepackage{url}

\title{Liam Giles}
\author{\url{liamthomasgiles1702@gmail.com}}
\date{07857317891}

\begin{document}

\maketitle
\thispagestyle{empty}

\subsection*{Personal Statement}
I am an energetic, motivated and driven person with a wide range of work and life experience. Studying a Bachelor's degree in Theoretical Physics, I have been able to develop excellent time management, team-working, and problem-solving skills. My BSc final year project and dissertation focused on the development of a bespoke Convolutional Neural Network (CNN) for the classification of image-like output data for a new type of opaque liquid particle detector, which was able to achieve unprecedented classification accuracy between electrons and gamma photons. This allowed me to land an internship at MeVitae, where I gained experience working on production-ready neural networks, web scraper algorithms and managing a back-end database for an internal automated lead generation tool for B2B sales.

Prior to and during my studies, I worked in a number of psychiatric hospitals with Cygnet Healthcare. During this time I learned invaluable interpersonal skills, interacting with and caring for individuals with a range of conditions, providing encouragement and practical assistance in their day-to-day lives.

\subsection*{Skills}
\begin{itemize}
    \item Highly proficient with Python (including Tensorflow, PyTorch, NumPy) and HTML, CSS, and JavaScript (including Canvas API, React, Next.js). Experience writing C\# for production-level code during my internship, and some familiarity with PHP, Go, Java and C.
    \item Deep knowledge of machine learning principles, with an emphasis on CNNs for image classification, fine-tuning and prompt engineering Large Language Models (LLMs), and word embeddings for text classification.
    \item Rich work experience has given me the communication skills to work professionally in any environment.
    \item Highest grades in university came from Thermal \& Statistical Physics ($>$90\%) and Condensed State Physics ($\sim$80\%).
    \item Proficient with Git and GitHub which have been used to keep track of all personal and work projects. See my public repositories at \url{https://www.github.com/liamtgiles17}.
    \item Experience in constructing technical reports with \LaTeX, and PowerPoint presentations documenting my work.
    \item Not afraid of working hard or going above and beyond for work I believe in, as evidenced by my current line of work and choice of degree course.
\end{itemize}

\subsection*{Employment}
\begin{itemize}
    \item \textbf{MeVitae - Project Delivery Assistant (Intern)}
    
        \textit{July 2024 and August - September 2024}

        \textit{Outline:} Worked closely with a supervisor to develop an internal automated sales tool, utilising web scraper algorithms, some API calls, and multiple statistical models/neural networks.
    \item \textbf{Cygnet Healthcare - Mental Health Support Worker}
    
        \textit{February 2019 - September 2020 and August 2023 - Present}

        \textit{Outline:} Delivering person-centered care to individuals with compassion and empathy, providing physical and emotional support and helping people re-gain control of their lives.
    \item \textbf{Just Eat - Delivery Driver}
    
        \textit{September 2021 - May 2023}

        \textit{Outline:} Ensuring food is delivered in a timely and efficient manner.
\end{itemize}

\subsection*{Education}
\begin{itemize}
    \item Graduated in BSc Theoretical Physics at the University of Sussex, achieving a final grade of 2(ii) (July 2024).
    \item 3 A-Levels at King Edward VI College, Stourbridge (2016-2018):
    \begin{itemize}
        \item Mathematics: A
        \item Physics: C
        \item Further Mathematics: D
    \end{itemize}
    \item 12 GCSEs at Dormston School, Dudley (2A*, 8A, 2B) (2011-2016).
\end{itemize}

\subsection*{Hobbies / Interests}
\begin{itemize}
    \item Study and play chess competitively with Mercia Chess Club.
    \item Train Brazilian Jiu-Jitsu.
    \item Recreational programming, in particular game and web development and implementing neural networks from scratch.
\end{itemize}

\end{document}
